\bf An Unitary RG-based Auxiliary Model Approach\\ to Strongly-Correlated Systems

### 2023-03-07 notes/notes.tex
cleaned up extra stuff

The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{W} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
\begin{equation}\begin{aligned}
	\label{bloch-states}
	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
\end{aligned}\end{equation}
where \(\lambda_{\ket{\vec k}}\) is a normalisation factor. To determine this, we compute the norm of the trail eigenstates:
\begin{equation}\begin{aligned}
	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
\end{aligned}\end{equation}
By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
\begin{equation}\begin{aligned}\label{zeroth_site_average}
	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
\end{aligned}\end{equation}
by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators. \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice. Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.

@@

\section{Analytic consistency check - On the Bethe lattice}
We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{W}\to\infty$ (the coordination number, and effectively the dimension). In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{W}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\). This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well. In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}. This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}. Applying the limit of \(w\to \infty\) on that equation gives
	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{W}} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1} 
where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model. It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\). Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}. From its definition in time domain, we have
	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}. We note that \(|G^{(0)}(\vec k, t)| \leq 1\). Using the Fourier transform  definition
	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
For a coordination number of \(\mathcal{W}\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\). Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{W}}\). In contrast, there is only one local Greens function, that for \(\vec r_i=0\). The local Greens function therefore scales independent of \(w\). This implies that 
	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).

\chapter{Going to larger clusters - the two site approach}

\section{Why expand the cluster?}
The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster:
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{aux} =  \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
\end{aligned}\end{equation}
This was able to describe an impurity phase transition from screened strong-coupling phase to local moment weak coupling phase, upon tuning \(U_b/J\). This then leads to a metal-insulator transition in the bulk, owing to the relations between the Greens functions and spectral functions obtained earlier. The single-site nature of the cluster (there was only a single impurity) has the following consequences:
\begin{itemize}
	\item [1.] The \(k-\)space self-energy of the bath has only minimal \(k-\)dependence arising from nearest-neighbour non-locality between the impurity and the zeroth site of the bath.
	\item [2.] The local moment phase (which reduces to a set of decoupled clusters) becomes just the atomic limit, because each cluster has just one impurity.
\end{itemize}

In this chapter, we will improve on these two points by considering a larger cluster that has two impurities interacting with each other:
\begin{equation}\begin{aligned}
	\label{dimer_ham}
	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
\end{aligned}\end{equation}
\(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer. They interact with each other through the same hopping parameter \(t\) as the bath. Each of the impurities has its own correlation \(U\) and hybridisation with the bath through \(V\) and \(J\). Each impurity site \(d_i\) couples with a bath site \(0_i\). \(0_1\) and \(0_2\) are assumed to be adjacent to each other, connected by the hopping \(t\). The setup is shown in fig.~\ref{two-imp-cluster}.

Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard-Heisenberg), but does not describe the physics of this new auxiliary model. That requires performing a renormalisation group calculation for \(H_\text{aux}\), and that will be provided at a later point in time.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\textwidth]{../figures/two-site-cluster.pdf}
	\caption{Two-impurity SIAM hybridising with a bath}
	\label{two-imp-cluster}
\end{figure}

\section{Solution of the Hubbard dimer using the Anderson molecule}
This section tries to see how far we can we can go if we just work with the Anderson molecule as the smallest unit of tiling. We will attempt to reproduce the entire spectrum of a Hubbard dimer by creating a new Hamiltonian made up purely of Anderson molecules. This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.

The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer. In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site. First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
	\label{hubb_dimer}
	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
	\label{and_dimer}
	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
\begin{itemize}
	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site. So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively. For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by. So, if \(d \to 1(2)\), then \(z \to 2(1)\).
	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site. Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.

The wavefunctions for the \(N=2\) sector can also be connected through these transformations. Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions [CITE PAVARINI]:
\begin{equation}\begin{aligned}
	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
\end{aligned}\end{equation}
where 
\begin{equation}\begin{aligned}
	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
\end{aligned}\end{equation}
$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
From the forms of the wavefunctions and eigenenergies, we can immediately write down
\begin{equation}\begin{aligned}
	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
\end{aligned}\end{equation}
This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector. These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\). In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime. This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime. Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.

\comment{
\section{Strategy by starting from a zero bandwidth model}
We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian. The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.

 To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity). We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath". The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath. \textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}. In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1. With all these steps, the Hamiltonian takes the form:
 \begin{equation}\begin{aligned}
 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp. \& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff. bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
 \end{aligned}\end{equation}
 \begin{figure}[!htb]
 	\centering
 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
 	\caption{Correlated asymmetric Anderson molecule schematic version. It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink). The other sites (green) form the rest of the bath. Just the impurity site and the zeroth site have onsite repulsion.}
 	\label{and_mol}
 \end{figure}
 This Hamiltonian is depicted in fig.~\ref{and_mol}. Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1). To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1. The resultant Hamiltonian is
 \begin{equation}\begin{aligned}
 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff. bath coupling} \\
 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
 \end{aligned}\end{equation}

 To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
 This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site. With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
 	\label{dimer_p_bat}
 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
 \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
 	\label{dimer_ham}
 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
 	\label{hubb-dim}
 This entire procedure is depicted in fig.~\ref{dimer-bath}.
 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian. We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian. In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice. We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
 	\label{dimer-bath} 
 We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice. The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice. We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
 What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model. If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
 where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian. 
 The existence of $U$ is contingent on how good the approximations are.

 We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
 \begin{itemize}
 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}. The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath. As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
 	\item We then perform a unitary RG on $H^A$. This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$. At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}. If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$. This constitutes the second approximation we make.
\end{itemize}
}

\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
\begin{equation}\begin{aligned}
	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
\end{aligned}\end{equation}
For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. For example, a square 2d lattice will have to be placed on a 2-torus.

>>>>

The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{W} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
\begin{equation}\begin{aligned}
	\label{bloch-states}
	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
\end{aligned}\end{equation}
where \(\lambda_{\ket{\vec k}}\) is a normalisation factor.

@@

\section{Analytic consistency check - On the Bethe lattice}
We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{W}\to\infty$ (the coordination number, and effectively the dimension). In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{W}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\). This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well. In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}. This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}. Applying the limit of \(w\to \infty\) on that equation gives
\begin{equation}\begin{aligned}
	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{W}} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1} 
\end{aligned}\end{equation}
where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model. It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
